The Poisson approximate likelihood compared to the particle filter

### 2024-08-21 ms.Rnw
gl results

\yize{ON AVERAGE PAL IS 25.3 LOG UNITS LOWER THAN PFILTER AND SHOULD WE MENTION THAT WE USED THE SIMULATED DATA WITHOUT ZEROS? \\ 
THE TABLE SEEMS TO BE TALL AND THIN. SHOULD WE PUT IT IN A APPENDIX?}

>>>>

\yize{ON AVERAGE PAL IS 25.3 LOG UNITS LOWER THAN PFILTER AND SHOULD WE MENTION THAT WE USED THE SIMULATED DATA WITHOUT ZEROS?}
